---
title: "Assignment 1"
author: "Dhiren Abichandani"
date: "1/23/2022"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r}
library(readr)
adult <- read_csv("adult.csv")
```{r}

# Imported the adult.csv file which is originally from my Business Analytics class last semester Fall 2021 where it was used for learning purposes.

```{r}
summary(adult)
```{r}

# Printed a summary of all the variables. Noticed that the character classes needed to be changed to categorical.

```{r}
adult$workclass = as.factor(adult$workclass)
adult$education = as.factor(adult$education)
adult$`marital-status` = as.factor(adult$`marital-status`)
adult$occupation = as.factor(adult$occupation)
adult$relationship = as.factor(adult$relationship)
adult$race = as.factor(adult$race)
adult$gender = as.factor(adult$gender)
adult$`native-country` = as.factor(adult$`native-country`)
adult$income = as.factor(adult$income)
```{r}

# Changed all character classes to categorical.

```{r}
summary(adult)
```{r}

# Printed a new summary of all the variables that were now either quantitative or categorical. 

```{r}
library(caret)
dummy_model <- dummyVars(~relationship, data = adult)
head(predict(dummy_model, adult))
```{r}

# Transformed the relationship categorical variable into dummy variables.

```{r}
library(dplyr)
age <- adult %>% group_by(age) %>% count(age)
colnames(age) <- c('Age','Count')
plot(age)
```{r}

# Created a scatter-plot of the quantitative variable age based on its count in the data-set.
